Social Visual Analytics: DevOps for Data Scientists

### 2015-03-24 discussion.tex
table

>>>>

\begin{table*}
  \centering
  \begin{tabular}{l|cccccc}
           & Versioning/Forking & Collaboration & Deployment & Multilanguage & Integrated Reports & Integrated Analysis \\
    \hline
RCloud     &       v            &       v       &     v      &      v        &           v        &           v         \\
RStudio    &                    &               &            &               &           v        &           v         \\
JSFiddle   &       v            &       v       &            &               &                    &                     \\
bl.ocks    &       v            &       v       &            &               &           v        &                     \\
shiny      &                    &               &     v      &               &           v        &           v         \\
Jupyter    &                    &               &            &      v        &           v        &           v         \\
Tableau    &                    &               &            &               &                    &                     
  \end{tabular}
  \caption{Comparison of system features.}
\end{table*}
